Seasonality in governing upper-ocean dynamics at submesoscales

### 2016-06-05 writeup/rocha_etal.tex
Edits figs
New supplemental figure
Edits captions of figures

@@

@@

\begin{figure*}[ht]
   \begin{center}
     \includegraphics[width=.9\textwidth]{figs/figA1.pdf}
  \caption{A near-surface KE spectra comparison between model and two
  available mooring observations.}
  \label{figA1}
  \end{center}
\end{figure*}

@@

@@

\begin{acknowledgments}
Thanks to the MITgcm usual suspects.
This research was funded by NSF and NASA.
\end{acknowledgments}

>>>>

\appendix

@@

\begin{figure*}[ht]
   \begin{center}
     \includegraphics[width=1.\textwidth]{figs/fig_s2_1.pdf}
  \caption{Potential density: a comparison between Roemmich-Gilson Argo
          climatology (a, b) and the LLC simulations 1/24$^\circ$ (c, d)
          and  1/48$^\circ$ (e, f). \textcolor{red}{Need to re-plot  the 1/24$^\circ$
          figures once extraction (currently down) becomes available}.}
  \label{figS2_1}
  \end{center}
\end{figure*}

\subsection{Spectra}

\begin{figure*}[ht]
   \begin{center}
     \includegraphics[width=1.\textwidth]{figs/fig_s2_3.pdf}
  \caption{A comparison between spectra of the two LLC simulations 1/24$^\circ$
  (green) and 1/48$^\circ$ (purple). The statistical errorbars represent conservative
  significance levels considering that there are only four independent relations
  for the monthly spectra.}
  \label{figS2_3}
  \end{center}
\end{figure*}

\subsection{Seasonality in statistics: probability density functions}
\begin{figure*}[ht]
   \begin{center}
     \includegraphics[width=1.\textwidth]{figs/fig_s2_2.pdf}
  \caption{Time dependence of probability density functions of vertical vorticity (a, b)
  and horizontal divergence (c, d). Monthly averages in April and October are
  also shown (e, f).}
  \label{figS2_2}
  \end{center}
\end{figure*}

@@

\begin{figure*}[ht]
   \begin{center}
     \includegraphics[width=.9\textwidth]{figs/figA1.pdf}
  \caption{A comparison between frequency spectra of LLC simulations and two
  available moored current meter records.}
  \label{figA1}
  \end{center}
\end{figure*}

@@

\begin{figure*}[ht]
   \begin{center}
     \includegraphics[width=1.\textwidth]{figs/fig_s3.pdf}
  \caption{The seasonal variability of the WOA 2013 stratification averaged  over
  the domain and the associated gravest three pressure modes. Only the upper 450 m is shown.}
  \label{figS3}
  \end{center}
\end{figure*}

@@

\begin{acknowledgments}
We thank the MITgcm community and our colleagues at the NASA Advanced
Supercomputing (NAS) Division for their awesome support.
This research was funded by NASA and NSF.
\end{acknowledgments}
